Affective Uplift During Video Game Play: A Naturalistic Case Study

### 2023-10-19 ms.Rmd
Add Zenodo link

The data and code we used to analyze it are available on GitHub (<https://github.com/digital-wellbeing/pws-prepost>) and archived at Zenodo (). Outputs of the computational notebooks are at (). For the full PWS dataset, see @vuorreIntensiveLongitudinalDataset2023.

@@

Estimated (changes) in mood as a function of session duration. Top: Average mood during a gaming session. Bottom: Change in mood during a session compared to mood at the beginning of a session. Gray ribbons indicate 95\\% confidence bands. We truncated the x-axis at three hours for this figure.

@@

Estimated (changes) in mood as a function of session duration and pre-play mood. Top. Mood for the average player during a gaming session with pre-play mood at 5th, 25th, 50th, and 75th percentiles (columns). Ribbons indicate 95\\% confidence. Bottom. Same as above but with change in mood on the y-axis.

>>>>

The data and code we used to analyze it are available on GitHub (<https://github.com/digital-wellbeing/pws-prepost>) and archived at Zenodo (<https://zenodo.org/doi/10.5281/zenodo.10021014>). For the full PWS dataset, see @vuorreIntensiveLongitudinalDataset2023.

@@

Estimated (changes) in mood as a function of session duration. Top: Average mood during a gaming session. Bottom: Change in mood during a session compared to mood at the beginning of a session. Gray ribbons indicate 95\% confidence bands. We truncated the x-axis at three hours for this figure.

@@

Estimated (changes) in mood as a function of session duration and pre-play mood. Top. Mood for the average player during a gaming session with pre-play mood at 5th, 25th, 50th, and 75th percentiles (columns). Ribbons indicate 95\% confidence. Bottom. Same as above but with change in mood on the y-axis.
